|

### 2022-11-04 manuscript.Rmd
add annotated bibliography

>>>>

# Lit Review

## @shinoharaWhoTeachesAccessibility2018

### RP

Industry demand for software developers with knowledge of accessibility has increased substantially in recent years. However, there is little knowledge about the prevalence of higher education teaching about accessibility or faculty's perceived barriers to teaching accessibility.

### RQ

### DC

we surveyed 14,176 computing and information science faculty in the United States. We received a representative sample of at least one response from 318 of the 352 institutions we surveyed, totaling 1,857 responses.

### Findings

175 institutions (50%) had at least one instructor teaching accessibility and that no fewer than 2.5% of faculty overall teach accessibility. Faculty that teach accessibility are twice as likely to be female, to have expertise in HCI and software engineering, and to know people with disabilities.

The most critical barriers to teaching accessibility that faculty reported were the absence of clear and discipline-specific accessibility learning objectives and the lack of faculty knowledge about accessibility.

Faculty desired resources that were specific to the areas of computing in which they teach rather than general accessibility resources and guidelines.
